sd_fig5

### 2020-07-06 examples/sd_fig5.Rmd
code for fig5 plots
fixed figures

```{r, cache=TRUE}
library(expm)
# System drift Figure 5 plot

@@

tt <- seq(0,6*pi, length.out=500)

@@

>>>>

```{r}
library(expm)
# System drift Figure 5 plot

@@

tt <- seq(0,6*2*pi, length.out=500)

@@

```{r, fig.width=2.5, fig.height=1.5, fig.align="center"}

C2 <- matrix(c(0,1), nrow=1)
h.2 <- function (t,tau=0,A=A_fn(tau)) { sapply(t, function (tt) C2 %*% expm(tt*A) %*% B) }

hhf00 <- sapply( list(A_fn(0)), function (A) { sapply(tt, h, A=A) } )
hh02 <- sapply( list(A_fn(0)), function (A) { sapply(tt, h.2, A=A) } )
hhn22 <- sapply( list(A_fn(-2)), function (A) { sapply(tt, h.2, A=A) } )

par(mar=c(4.5, 4, 1, 1)+.1)
plot(tt, hhf00, type="l", lwd=2, ylab= expression("phenotype" ~ phi(t)), xlab="time t", col="steelblue4", ylim=c(-3,3), cex.lab=1)

par(mar=c(4.5, 4, 1, 1)+.1)
plot(tt, hhf00, type="l", lwd=2, ylab= expression("kryptotype" ~ kappa(t)), xlab="time t", col="steelblue4", ylim=c(-3,3), cex.lab=1)
lines(tt, hhn22, lwd=2, col="seagreen")
lines(tt, hh02, lwd=2, col="red4")
```
